### 2014-11-12 sssp.tex
spacing

Here we add coordination to the SSSP program described in Section
The coordinated version of the
SSSP~(Fig.~\ref{code:shortest_path_program_coord}) uses the coordination fact
\texttt{set-priority} (line 14). We also use a global program directive to order
priorities in ascending order (line 5).

@@

Figure~\ref{results:sssp_uspowergrid} shows experimental results when the
program computes the SSSP for 20\% of the nodes of the graph.
There are some situations where unnecessary facts are propagated
because although the shortest distance is selected locally, sub-optimal distances may be
propagated because many SSSP distances are computed at the same time.
However, we see a reduction of over 50\% in the number of
derived facts when using the coordinated version \textbf{C} over the regular
version \textbf{R}. The results also show that the coordinated
version using 16 threads is 1.3 times faster than the regular version using 16
threads while still showing good scaling.

\begin{topfig}
   \begin{center}
      \subfloat[]{ \begin{tabular}[b]{ | c | c | c | }
         \hline                       
         \textbf{\# T} & \textbf{R} & \textbf{C} \\ \hline \hline
         1 & 333K & 206K \\
         2 & 300K & 210K \\
         4 & 316K & 208K \\
         8 & 328K & 211K \\
         16 & 343K & 212K \\
         \hline  
         \end{tabular}
         \normalsize
      }
      \subfloat[]{\includegraphics[width=5.5cm]{results/shortest-uspowergrid.png}}
   \end{center}
   \scap{results:sssp_uspowergrid}{Experimental results for the SSSP program using US power grid network.
   On the left we show the number of facts derived for the regular \textbf{R}
   and coordinated version \textbf{C} using a variable number of threads
   \textbf{\# T}. On the right, we have the scalability of the regular and
   coordinated version. The speedup values are computed using the execution
   time for 1 thread.}
\end{topfig}

>>>>

Here we add coordination to the SSSP program described in \sectref{sect:ssspex}.
The coordinated version of the
SSSP~(Fig.~\ref{code:shortest_path_program_coord}) uses the coordination fact
\texttt{set-priority} (line 14). We also use a global program directive to order
priorities in ascending order (line 5).

@@

Fig.~\ref{results:sssp_uspowergrid} shows experimental results when the
program computes the SSSP for 20\% of the nodes of the graph.
There are some situations where unnecessary facts are propagated
because although the shortest distance is selected locally, sub-optimal distances may be
propagated because many SSSP distances are computed at the same time.
However, we see a reduction of over 50\% in the number of
derived facts when using the coordinated version \textbf{C} over the regular
version \textbf{R}. The results also show that the coordinated
version using 16 threads is 1.3 times faster than the regular version using 16
threads while still showing good scaling.

\begin{topfig}
\vspace*{-5ex}
   \begin{center}
      \subfloat[]{ \begin{tabular}[b]{ | c | c | c | }
         \hline                       
         \textbf{\# T} & \textbf{R} & \textbf{C} \\ \hline \hline
         1 & 333K & 206K \\
         2 & 300K & 210K \\
         4 & 316K & 208K \\
         8 & 328K & 211K \\
         16 & 343K & 212K \\
         \hline  
         \end{tabular}
         \normalsize
      }
      \subfloat[]{\includegraphics[width=5cm]{results/shortest-uspowergrid.png}}
   \end{center}
   \scap{results:sssp_uspowergrid}{Results for SSSP run on the 
   US power grid network.  On the left we show the number of facts
   derived for the regular \textbf{R} and coordinated
   version \textbf{C} using a variable number of threads \textbf{\#
   T}. On the right, we show the scalability of the regular and
   coordinated version. The speedup values are computed using the
   execution time for 1 thread.}
\vspace*{-3ex plus 0pt minus 1ex}
\end{topfig}
